---
title: "Covid Daily Report"
author: "Andrew F. Griffin"
date: "10/29/2020"
output: html_document
---
```{r US GRAPH, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
library(zoo)
library(lubridate)
library(janitor)

library(ggplot2)
library(gghighlight)
library(ggrepel)
library(ggthemes)
library(RColorBrewer)
library(viridis)
library(paletteer)
library(usmap)
library(grid)
library(gridExtra)

library(gt)
library(markdown)
library(pracma)


# LOAD DATA
load("rda/covid_us_sum.rda")
load("rda/covid_us_growth.rda")
load("rda/theme_DataStache.rda")
options(scipen = 999)


#### US DAILY GRAPHS ####
p_US_new_case_plot <- covid_us_sum %>% 
  ggplot(aes(date, new_cases)) +
  geom_hline(yintercept=0, col = "grey40", size = .2) +
  geom_bar(stat = "identity", fill="blue", alpha = .3, size = .1) +
  scale_color_manual(values="light grey") +
  geom_line(aes(y = new_cases_07da), size = .35, col="blue") +
  xlab("Date") +
  ylab("New Total Cases") +
  ggtitle("US Total New Cases") +
  labs(caption = "Created by Andrew F. Griffin\nCovid Data from The Covid Tracking Project") +
  scale_x_date(date_labels = "%b", breaks= "1 month", expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  coord_cartesian(xlim = c(ymd(20200301), NA), ylim = c(0, max(covid_us_sum$new_cases_07da, na.rm = TRUE) * 1.1)) +
  theme_DataStache() +
  theme(text = element_text(size = rel(.6)))

p_US_new_test_plot <- covid_us_sum %>%
  ggplot(aes(date, new_tests)) +
  geom_hline(yintercept=0, col = "grey40", size = .2) +
  geom_bar(stat = "identity", fill="dark green", alpha = .3, size = .1) +
  scale_color_manual(values="light grey") +
  geom_line(aes(y = new_tests_07da), size = .35, col="dark green") +
  xlab("Date") +
  ylab("New Total Tests") +
  ggtitle("US Total New Tests") +
  labs(caption = "Created by Andrew F. Griffin\nCovid Data from The Covid Tracking Project") +
  scale_x_date(date_labels = "%b", breaks= "1 month", expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  coord_cartesian(xlim = c(ymd(20200301), NA), ylim = c(0, max(covid_us_sum$new_tests_07da, na.rm = TRUE) * 1.1)) +
  theme_DataStache() +
  theme(text = element_text(size = rel(.6)))

p_US_new_deaths_plot <- covid_us_sum %>%
  ggplot(aes(date, new_death)) +
  geom_hline(yintercept=0, col = "grey40", size = .2) +
  geom_bar(stat = "identity", fill="dark red", alpha = .3, size = .1) +
  scale_color_manual(values="light grey") +
  geom_line(aes(y = new_death_07da), size = .35, col="dark red") +
  xlab("Date") +
  ylab("New Total Deaths") +
  ggtitle("US Total New Deaths") +
  labs(caption = "Created by Andrew F. Griffin\nCovid Data from The Covid Tracking Project") +
  scale_x_date(date_labels = "%b", breaks= "1 month", expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  coord_cartesian(xlim = c(ymd(20200301), NA), ylim = c(0, max(covid_us_sum$new_death_07da, na.rm = TRUE) * 1.1)) +
  theme_DataStache() +
  theme(text = element_text(size = rel(.6)))

p_US_percent_pos <- covid_us_sum %>%
  ggplot(aes(date, percent_pos)) +
  geom_hline(yintercept=0, col = "grey40", size = .2) +
  geom_bar(stat = "identity", fill="deepskyblue4", alpha = .3, size = .1) +
  scale_color_manual(values="light grey") +
  geom_line(aes(y = percent_pos_07da), size = .35, col="deepskyblue4") +
  xlab("Date") +
  ylab("Percent Positive") +
  ggtitle("US Percent Positive") +
  labs(caption = "Created by Andrew F. Griffin\nCovid Data from The Covid Tracking Project") +
  scale_x_date(date_labels = "%b", breaks= "1 month", expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  coord_cartesian(xlim = c(ymd(20200301), NA), ylim = c(0, max(covid_us_sum$percent_pos_07da, na.rm = TRUE) * 1.1)) +
  theme_DataStache() +
  theme(text = element_text(size = rel(.6)))

p_US_hosp <- covid_us_sum %>%
  ggplot(aes(date, cur_hosp)) +
  geom_hline(yintercept=0, col = "grey40", size = .2) +
  geom_bar(stat = "identity", fill="orange4", alpha = .3, size = .1) +
  scale_color_manual(values="light grey") +
  geom_line(aes(y = cur_hosp_07da), size = .35, col="orange4") +
  xlab("Date") +
  ylab("Percent Positive") +
  ggtitle("US Hospitalization") +
  labs(caption = "Created by Andrew F. Griffin\nCovid Data from The Covid Tracking Project") +
  scale_x_date(date_labels = "%b", breaks= "1 month", expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  coord_cartesian(xlim = c(ymd(20200301), NA), ylim = c(0, max(covid_us_sum$cur_hosp_07da, na.rm = TRUE) * 1.1)) +
  theme_DataStache() +
  theme(text = element_text(size = rel(.6)))

p_US_new_hosp <- covid_us_sum %>%
  ggplot(aes(date, new_hosp)) +
  geom_hline(yintercept=0, col = "grey40", size = .2) +
  geom_bar(stat = "identity", fill="orange4", alpha = .3, size = .1) +
  scale_color_manual(values="light grey") +
  geom_line(aes(y = new_hosp_07da), size = .35, col="orange4") +
  xlab("Date") +
  ylab("Percent Positive") +
  ggtitle("US New Hospitalization") +
  labs(caption = "Created by Andrew F. Griffin\nCovid Data from The Covid Tracking Project") +
  scale_x_date(date_labels = "%b", breaks= "1 month", expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  coord_cartesian(xlim = c(ymd(20200301), NA), ylim = c(min(covid_us_sum$new_hosp_07da, na.rm = TRUE) * 1.1, max(covid_us_sum$new_hosp_07da, na.rm = TRUE) * 1.1)) +
  theme_DataStache() +
  theme(text = element_text(size = rel(.6)))

grid.arrange(p_US_new_case_plot, p_US_new_test_plot, p_US_hosp, p_US_new_deaths_plot, p_US_percent_pos, p_US_new_hosp, nrow=2)
```
<br></br>
<br></br>
```{r DAILY SUMMARY, warning=FALSE, echo=FALSE, message=FALSE}
# LOAD DATA
load("rda/covid_us_sum.rda")
load("rda/ind_tywm_date.rda")

### USA TABLE
covid_us_sum %>%
  select(date,
         new_cases,
         new_cases_07da,
         new_tests,
         percent_pos,
         new_death,
         new_death_07da,
         cur_hosp,
         new_hosp) %>%
  filter(date %in% ind_tywm_date) %>%
  gt() %>% 
  ## LABELS STUB / TITLE / SUBTITLE
  tab_options(table.font.size = pct(75)) %>%
  tab_header(title = md("**TOTAL COVID REPORTS IN THE USA**"),  
             subtitle = md("*Today, Yesterday, Last Week, Last Month*")) %>%
  ## RENAMES COLUMNS
  cols_label(date = md("**Date**"), 
             new_cases = md("**New Cases**"),
             new_cases_07da = md("**New Cases Avg**"),
             new_tests = md("**New Tests**"),
             percent_pos = md("**Percent Positive**"),
             new_death = md("**New Deaths**"),
             new_death_07da = md("**New Deaths Avg**"),
             cur_hosp = md("**Hospitalization**"),
             new_hosp = md("**New Hosp.**")) %>%
  fmt_percent(columns = vars(percent_pos),
              decimals = 1) %>%
  cols_align(align = "center") %>%
  ## FORMATS DATA
  fmt_number(columns =  vars(new_cases,
                             new_cases_07da,
                             new_tests,
                             new_death_07da,
                             cur_hosp,
                             new_hosp),
             decimals = 0) %>%
  ## BOLD STATES COLUMN
  tab_style(style = list(cell_text(weight = "bold")),
            locations = cells_body(columns = vars(date))) %>% 
  ## STRIPING
  opt_row_striping(row_striping = TRUE) %>%
  tab_source_note(source_note = md("*Created by Andrew F. Griffin, Data from The Covid Tracking Project*"))
```
<br></br>

Covid Data for `r month(covid_us_sum$date[1], label = TRUE)` `r day(covid_us_sum$date[1])`  
New Cases  
Tdy (`r month(covid_us_sum$date[1])`-`r day(covid_us_sum$date[1])`): `r format(covid_us_sum$new_cases[1], big.mark = ",")` `r ifelse(covid_us_sum$new_cases[1] == max(covid_us_sum$new_cases), "*", "")`  
Yest (`r month(covid_us_sum$date[2])`-`r day(covid_us_sum$date[2])`): `r format(covid_us_sum$new_cases[2], big.mark = ",")`  
Lt Wk (`r month(covid_us_sum$date[8])`-`r day(covid_us_sum$date[8])`): `r format(covid_us_sum$new_cases[8], big.mark = ",")`  
<br></br>
New Tests  
T: `r format(covid_us_sum$new_tests[1], big.mark = ",")` `r ifelse(covid_us_sum$new_tests[1] == max(covid_us_sum$new_tests), "*", "")`  
Y: `r format(covid_us_sum$new_tests[2], big.mark = ",")`  
LW: `r format(covid_us_sum$new_tests[8], big.mark = ",")`  
<br></br>
Percent Positive  
T: `r covid_us_sum$percent_pos[1]*100`%  
Y: `r covid_us_sum$percent_pos[2]*100`%  
LW: `r covid_us_sum$percent_pos[8]*100`%  
<br></br>
New Deaths  
T: `r format(covid_us_sum$new_death[1], big.mark = ",")` `r ifelse(covid_us_sum$new_death[1] == max(covid_us_sum$new_death), "*", "")`  
Y: `r format(covid_us_sum$new_death[2], big.mark = ",")`  
LW: `r format(covid_us_sum$new_death[8], big.mark = ",")`  
* = Record  
<br></br>
The Last Time Things were this bad:
```{r CASES THIS HIGH, warning=FALSE, echo=FALSE, message=FALSE}
covid_us_sum %>%
  filter(new_cases >= covid_us_sum$new_cases[1]) %>% select(date, new_cases)
```

```{r 7DA CASES THIS HIGH, warning=FALSE, echo=FALSE, message=FALSE}
covid_us_sum %>%
  filter(new_cases_07da >= covid_us_sum$new_cases_07da[1]) %>% select(date, new_cases_07da)
```

```{r DEATHS THIS HIGH, warning=FALSE, echo=FALSE, message=FALSE}
covid_us_sum %>%
  filter(new_death >= covid_us_sum$new_death[1]) %>% select(date, new_death)
```

```{r 7DA DEATHS THIS HIGH, warning=FALSE, echo=FALSE, message=FALSE}
covid_us_sum %>%
  filter(new_death_07da >= covid_us_sum$new_death_07da[1]) %>% select(date, new_death_07da)
```

```{r HOSP THIS HIGH, warning=FALSE, echo=FALSE, message=FALSE}
covid_us_sum %>%
  filter(cur_hosp >= covid_us_sum$cur_hosp[1]) %>% select(date, cur_hosp)
```

```{r NEW HOSP THIS HIGH, warning=FALSE, echo=FALSE, message=FALSE}
covid_us_sum %>%
  filter(new_hosp >= covid_us_sum$new_hosp[1]) %>% select(date, new_hosp)
```

```{r NEW HOSP 07DA THIS HIGH, warning=FALSE, echo=FALSE, message=FALSE}
covid_us_sum %>%
  filter(new_hosp >= covid_us_sum$new_hosp_07da[1]) %>% select(date, new_hosp_07da)
```
<br></br>
```{r WEEKLY SUMMARIES, warning=FALSE, echo=FALSE, message=FALSE}
# LOAD DATA
load("rda/covid_us_growth.rda")

### USA TABLE
covid_us_growth %>%
  select(weeks,
         sum_new_cases,
         sum_new_tests,
         mean_percent_pos,
         sum_new_death) %>%
  gt() %>% 
  ## LABELS STUB / TITLE / SUBTITLE
  tab_options(table.font.size = pct(75)) %>%
  tab_header(title = md("**COVID GROWTH IN THE USA**"),  
             subtitle = md("*Comparing the Last Two Weeks*")) %>%
  ## RENAMES COLUMNS
  cols_label(weeks = md("**Weeks**"), 
             sum_new_cases = md("**Total New Cases**"),
             sum_new_tests = md("**Total New Tests**"),
             mean_percent_pos = md("**Average Percent Positive**"),
             sum_new_death = md("**New Deaths**")) %>%
  fmt_percent(columns = vars(mean_percent_pos),
              decimals = 1) %>%
  cols_align(align = "center") %>%
  ## FORMATS DATA
  fmt_number(columns =  vars(sum_new_cases,
                             sum_new_tests,
                             sum_new_death),
             decimals = 0) %>%
  ## BOLD STATES COLUMN
  tab_style(style = list(cell_text(weight = "bold")),
            locations = cells_body(columns = vars(weeks))) %>% 
  ## STRIPING
  opt_row_striping(row_striping = TRUE) %>%
  tab_source_note(source_note = md("*Created by Andrew F. Griffin, Data from The Covid Tracking Project*"))
```
<br></br>
<br></br>
```{r US STATES by CASES, echo=FALSE, message=FALSE, warning=FALSE}
# LOAD DATA
load("rda/covid_state_growth.rda")
load("rda/covid_state_zones.rda")

covid_state_table <- covid_state_growth %>%
  left_join(covid_state_zones) %>%
  arrange(desc(sum_cases_percap)) %>%
  mutate(rank = order(desc(sum_cases_percap)))

### USA TABLE
covid_state_table %>%
  select(state_name,
         rank,
         sum_cases_percap,
         sum_tests_percap,
         percent_pos,
         sum_death_percap,
         cases_zone,
         percent_zone) %>%
  gt() %>% 
  ## LABELS STUB / TITLE / SUBTITLE
  tab_options(table.font.size = pct(75)) %>%
  tab_header(title = md("**COVID GROWTH BY STATE ORDERED BY CASES**"),  
             subtitle = md("*Totals Per 100k People in the Last Week*")) %>%
  ## RENAMES COLUMNS
  cols_label(state_name = md("**State**"),
             rank = md("**Rank**"),
             sum_cases_percap = md("**New Cases**"),
             sum_tests_percap = md("**New Tests**"),
             percent_pos = md("**Percent Positive**"),
             sum_death_percap = md("**New Deaths**"),
             cases_zone = md("**Zone by Cases**"),
             percent_zone = md("**Zone by Positivity**")) %>%
  fmt_percent(columns = vars(percent_pos),
              decimals = 1) %>%
  cols_align(align = "center") %>%
  ## FORMATS DATA
  fmt_number(columns =  vars(sum_cases_percap,
                             sum_tests_percap,
                             sum_death_percap),
             decimals = 0) %>%
  ## BOLD STATES COLUMN
  tab_style(style = list(cell_text(weight = "bold")),
            locations = cells_body(columns = vars(state_name))) %>% 
  ## STRIPING
  opt_row_striping(row_striping = TRUE) %>%
  tab_source_note(source_note = md("*Created by Andrew F. Griffin, Data from The Covid Tracking Project*"))
```
<br></br>
```{r US STATES by POSITIVE, echo=FALSE, message=FALSE, warning=FALSE}
# LOAD DATA
load("rda/covid_state_growth.rda")
load("rda/covid_state_zones.rda")

covid_state_table <- covid_state_growth %>%
  left_join(covid_state_zones) %>%
  arrange(desc(percent_pos))%>%
  mutate(rank = order(desc(percent_pos)))

### USA TABLE
covid_state_table %>%
  select(state_name,
         rank,
         sum_cases_percap,
         sum_tests_percap,
         percent_pos,
         sum_death_percap,
         cases_zone,
         percent_zone) %>%
  gt() %>% 
  ## LABELS STUB / TITLE / SUBTITLE
  tab_options(table.font.size = pct(75)) %>%
  tab_header(title = md("**COVID GROWTH BY STATE ORDERED BY POSITVIES**"),  
             subtitle = md("*Totals Per 100k People in the Last Week*")) %>%
  ## RENAMES COLUMNS
  cols_label(state_name = md("**State**"),
             rank = md("**Rank**"),
             sum_cases_percap = md("**New Cases**"),
             sum_tests_percap = md("**New Tests**"),
             percent_pos = md("**Percent Positive**"),
             sum_death_percap = md("**New Deaths**"),
             cases_zone = md("**Zone by Cases**"),
             percent_zone = md("**Zone by Positivity**")) %>%
  fmt_percent(columns = vars(percent_pos),
              decimals = 1) %>%
  cols_align(align = "center") %>%
  ## FORMATS DATA
  fmt_number(columns =  vars(sum_cases_percap,
                             sum_tests_percap,
                             sum_death_percap),
             decimals = 0) %>%
  ## BOLD STATES COLUMN
  tab_style(style = list(cell_text(weight = "bold")),
            locations = cells_body(columns = vars(state_name))) %>% 
  ## STRIPING
  opt_row_striping(row_striping = TRUE) %>%
  tab_source_note(source_note = md("*Created by Andrew F. Griffin, Data from The Covid Tracking Project*"))
```
